\hypertarget{namespace_p_h_p_mailer}{}\section{P\+H\+P\+Mailer-\/\+Namensbereichsreferenz}
\label{namespace_p_h_p_mailer}\index{P\+H\+P\+Mailer@{P\+H\+P\+Mailer}}


\subsection{Ausführliche Beschreibung}
\mbox{\hyperlink{class_p_h_p_mailer}{P\+H\+P\+Mailer}} -\/ P\+HP email creation and transport class. P\+HP Version 5

\mbox{\hyperlink{}{The P\+H\+P\+Mailer Git\+Hub project  Marcus Bointon (Synchro/coolbru) \href{mailto:phpmailer@synchromedia.co.uk}{\tt phpmailer@synchromedia.\+co.\+uk}  Jim Jagielski (jimjag) \href{mailto:jimjag@gmail.com}{\tt jimjag@gmail.\+com}  Andy Prevost (codeworxtech) \href{mailto:codeworxtech@users.sourceforge.net}{\tt codeworxtech@users.\+sourceforge.\+net}  Brent R. Matzelle (original founder)  2012 -\/ 2014 Marcus Bointon  2010 -\/ 2012 Jim Jagielski  2004 -\/ 2009 Andy Prevost  \href{http://www.gnu.org/copyleft/lesser.html}{\tt http\+://www.\+gnu.\+org/copyleft/lesser.\+html} G\+NU Lesser General Public License  This program is distributed in the hope that it will be useful -\/ W\+I\+T\+H\+O\+UT A\+NY W\+A\+R\+R\+A\+N\+TY; without even the implied warranty of M\+E\+R\+C\+H\+A\+N\+T\+A\+B\+I\+L\+I\+TY or F\+I\+T\+N\+E\+SS F\+OR A P\+A\+R\+T\+I\+C\+U\+L\+AR P\+U\+R\+P\+O\+SE. P\+H\+P\+Mailer -\/ P\+HP email creation and transport class.  Marcus Bointon (Synchro/coolbru) \href{mailto:phpmailer@synchromedia.co.uk}{\tt phpmailer@synchromedia.\+co.\+uk}  Jim Jagielski (jimjag) \href{mailto:jimjag@gmail.com}{\tt jimjag@gmail.\+com}  Andy Prevost (codeworxtech) \href{mailto:codeworxtech@users.sourceforge.net}{\tt codeworxtech@users.\+sourceforge.\+net}  Brent R. Matzelle (original founder) P\+H\+P\+Mailer exception handler P\+H\+P\+Mailer P\+O\+P-\/\+Before-\/\+S\+M\+TP Authentication Class. P\+HP Version 5  \href{https://github.com/PHPMailer/PHPMailer/}{\tt https\+://github.\+com/\+P\+H\+P\+Mailer/\+P\+H\+P\+Mailer/}  Marcus Bointon (Synchro/coolbru) \href{mailto:phpmailer@synchromedia.co.uk}{\tt phpmailer@synchromedia.\+co.\+uk}  Jim Jagielski (jimjag) \href{mailto:jimjag@gmail.com}{\tt jimjag@gmail.\+com}  Andy Prevost (codeworxtech) \href{mailto:codeworxtech@users.sourceforge.net}{\tt codeworxtech@users.\+sourceforge.\+net}  Brent R. Matzelle (original founder)  2012 -\/ 2014 Marcus Bointon  2010 -\/ 2012 Jim Jagielski  2004 -\/ 2009 Andy Prevost  \href{http://www.gnu.org/copyleft/lesser.html}{\tt http\+://www.\+gnu.\+org/copyleft/lesser.\+html} G\+NU Lesser General Public License  This program is distributed in the hope that it will be useful -\/ W\+I\+T\+H\+O\+UT A\+NY W\+A\+R\+R\+A\+N\+TY; without even the implied warranty of M\+E\+R\+C\+H\+A\+N\+T\+A\+B\+I\+L\+I\+TY or F\+I\+T\+N\+E\+SS F\+OR A P\+A\+R\+T\+I\+C\+U\+L\+AR P\+U\+R\+P\+O\+SE. P\+H\+P\+Mailer P\+O\+P-\/\+Before-\/\+S\+M\+TP Authentication Class. Specifically for P\+H\+P\+Mailer to use for R\+F\+C1939 P\+O\+P-\/before-\/\+S\+M\+TP authentication. Does not support A\+P\+OP.  Richard Davey (original author) \href{mailto:rich@corephp.co.uk}{\tt rich@corephp.\+co.\+uk}  Marcus Bointon (Synchro/coolbru) \href{mailto:phpmailer@synchromedia.co.uk}{\tt phpmailer@synchromedia.\+co.\+uk}  Jim Jagielski (jimjag) \href{mailto:jimjag@gmail.com}{\tt jimjag@gmail.\+com}  Andy Prevost (codeworxtech) \href{mailto:codeworxtech@users.sourceforge.net}{\tt codeworxtech@users.\+sourceforge.\+net} P\+H\+P\+Mailer R\+F\+C821 S\+M\+TP email transport class. P\+HP Version 5  \href{https://github.com/PHPMailer/PHPMailer/}{\tt https\+://github.\+com/\+P\+H\+P\+Mailer/\+P\+H\+P\+Mailer/} The P\+H\+P\+Mailer Git\+Hub project  Marcus Bointon (Synchro/coolbru) \href{mailto:phpmailer@synchromedia.co.uk}{\tt phpmailer@synchromedia.\+co.\+uk}  Jim Jagielski (jimjag) \href{mailto:jimjag@gmail.com}{\tt jimjag@gmail.\+com}  Andy Prevost (codeworxtech) \href{mailto:codeworxtech@users.sourceforge.net}{\tt codeworxtech@users.\+sourceforge.\+net}  Brent R. Matzelle (original founder)  2014 Marcus Bointon  2010 -\/ 2012 Jim Jagielski  2004 -\/ 2009 Andy Prevost  \href{http://www.gnu.org/copyleft/lesser.html}{\tt http\+://www.\+gnu.\+org/copyleft/lesser.\+html} G\+NU Lesser General Public License  This program is distributed in the hope that it will be useful -\/ W\+I\+T\+H\+O\+UT A\+NY W\+A\+R\+R\+A\+N\+TY; without even the implied warranty of M\+E\+R\+C\+H\+A\+N\+T\+A\+B\+I\+L\+I\+TY or F\+I\+T\+N\+E\+SS F\+OR A P\+A\+R\+T\+I\+C\+U\+L\+AR P\+U\+R\+P\+O\+SE. P\+H\+P\+Mailer R\+F\+C821 S\+M\+TP email transport class. Implements R\+FC 821 S\+M\+TP commands and provides some utility methods for sending mail to an S\+M\+TP server.  Chris Ryan  Marcus Bointon \href{mailto:phpmailer@synchromedia.co.uk}{\tt phpmailer@synchromedia.\+co.\+uk} }}